\myTitle

### 2024-08-16 tex/body-text-of-paper.tex
Update major and minor Structure modes

The program STRUCTURE clustered fish at all values of $K$ from 2 to 7.
(Fig.~\ref{fig:struct}).  The clusters generally corresponded to groupings of related populations, and confirmed
{\em a priori} knowledge about which collections in the baseline could and should be
grouped together into reporting units.  At every value of $K$ CLUMPAK discerned \comment{at least
11 of 20 replicates} in the major mode (Fig.~\ref{fig:struct}).   
\comment{Need to add more description of the patterns, especially at $K=7$.}
\comment{Clustering solutions in the minor
modes appear in Fig.~\ref{fig:minor-modes}, which likely needs to be updated.  Get all this done
when AC is back and can vet it.}
%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\newcommand{\structcap}{\footnotesize Major modes found by STRUCTURE and summarized
by CLUMPAK out of 20 replicates for each value of $K$, the assumed number of
subpopulations. }
\begin{center}
\includegraphics[width=\columnwidth]{images/clumpak-crop.pdf}
\end{center}
\caption[\structcap]{\structcap}
\label{fig:struct}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The program STRUCTURE clustered fish at all values of $K$ from 2 to 7.
(Fig.~\ref{fig:struct}).  The clusters generally corresponded to groupings of related populations, and confirmed
{\em a priori} knowledge about which collections in the baseline could and should be
grouped together into reporting units.  At every value of $K$ CLUMPAK discerned at least
12 of 20 replicates in the major mode (Fig.~\ref{fig:struct}).   
\comment{Need to add more description of the patterns, especially at $K=7$.}
Clustering solutions in the minor
modes appear in Fig.~\ref{fig:minor-modes}, which likely needs to be updated.  Get all this done
when AC is back and can vet it.
%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\newcommand{\structcap}{\footnotesize Major modes found by STRUCTURE and summarized
by CLUMPAK out of 20 replicates for each value of $K$, the assumed number of
subpopulations. $K$ value is listed at lower right of each barplot, followed by the number
of replicate runs of structure that converged to this major mode.}
\begin{center}
\includegraphics[width=\columnwidth]{images/clumpak-crop.pdf}
\end{center}
\caption[\structcap]{\structcap}
\label{fig:struct}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-08-16 tex/supplemental-figures.tex
Include full WRAP description
Update major and minor Structure modes

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/num-alle-barplot.pdf}
\end{center}
\caption[Number of loci with different
total numbers of alleles]{\footnotesize Number of loci with different
total numbers of alleles in the data set. The one amplicon with only
one allele is {\tt Ots\_coho001\_05\_32691399}, which is fixed for alternate
in Chinook vs.\ coho salmon. It is helpful in identifying coho samples that are
misidentified during sampling as Chinook salmon.}
\label{fig:num-alle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/minor-modes-crop.pdf}
\end{center}
\caption[STRUCTURE minor modes found by CLUMPAK]{\footnotesize At each value of $K$
for which a minor mode was found, these plots show them}
\label{fig:minor-modes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth]{images/wrap-candi.pdf}
\caption[
	61 candidates for primer design for winter-run-associated polymorphisms
]{
	\footnotesize Genomic positions and values of $|d|$ (absolute difference in
	allele frequency between winter run and non-winter run fish of the CCV)
	for the 61 candidate SNPs (in red) to design for winter-run-associated polymorphisms
	(WRAPs).  Other sites are shown in black.  The $x$-axis shows position on
	each chromsome in the Otsh\_v1.0 assembly.  The chromsome name is indicated in the facet headers by
	RefSeq name
}
\label{fig:wrap-slide-window}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/num-alle-barplot.pdf}
\end{center}
\caption[Number of loci with different
total numbers of alleles]{\footnotesize Number of loci with different
total numbers of alleles in the data set. The one amplicon with only
one allele is {\tt Ots\_coho001\_05\_32691399}, which is fixed for alternate alleles
in Chinook vs.\ coho salmon. It is helpful in identifying coho samples that are
misidentified during sampling as Chinook salmon.}
\label{fig:num-alle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/minor-modes-crop.pdf}
\end{center}
\caption[STRUCTURE minor modes found by CLUMPAK]{\footnotesize STRUCTURE minor modes found by CLUMPAK.
At each value of $K$ for which a minor mode was found, the plot is shown.  $K$ values and number of times each minor
mode appeared out of 20 replicate runs of STRUCTURE appear to the lower right of each.}
\label{fig:minor-modes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth]{images/wrap-candi.pdf}
\caption[
	61 candidates for primer design for winter-run-associated polymorphisms
]{
	\footnotesize Genomic positions and values of $|d|$ (absolute difference in
	allele frequency between winter run and non-winter run fish of the CCV)
	for the 61 candidate SNPs (in red) to design for winter-run-associated polymorphisms
	(WRAPs).  Other sites are shown in black.  The $x$-axis shows position on
	each chromsome in the Otsh\_v1.0 assembly.  The chromsome name is indicated in the facet headers by
	RefSeq name
}
\label{fig:wrap-candi}
\end{figure}

### 2024-08-16 tex/supplemental-text.tex
Update major and minor Structure modes

\section{Winter-run-associated polymorphism (WRAP) methods and results\label{sec:wrap-methods}}

@@

%% Note to self.  The next section is documented in the project at:
%% /Users/eriq/Documents/work/assist/anthony_clemento/WRAP-crunching
These 48 amplicons were amplified and sequenced in 192 fish---96 Feather River spring run
and 96 winter run---on a MiSeq sequencer, and the variants were called using
GATK.  The resulting VCF file was used to estimate allele frequency differences between
winter run and feather river spring.  We also processed the sequence data using
microhaplot (\url{https://github.com/ngthomas/microhaplot}) and visually inspected
loci for consisten allele depth ratio and numbers of haplotypes.  We then chose 24 amplicons for further
testing on the basis of allele frequency differences between Feather River spring run and
winter run, number of haplotypes, and ease of scoring.  These 24 markers were typed on
a variety of fish over the course of a year, and we finally chose three to include in
our California Chinook reference baseline: one amplicon on each of chromosomes
8, 12, and 16.  The estimated frequencies of all the alleles present in the reference baseline
in those three amplicons appears shows that there are not fixed differences between
winter run and all other reporting units (Table~\ref{tab:wrap-freqs}).

>>>>

\section{Winter-run-associated polymorphism methods and results\label{sec:wrap-methods}}

@@

%% Note to self.  The next section is documented in the project at:
%% /Users/eriq/Documents/work/assist/anthony_clemento/WRAP-crunching
These 48 amplicons were amplified and sequenced in 192 fish---96 Feather River spring run
and 96 winter run---on a MiSeq sequencer, and the variants were called using
GATK.  The resulting VCF file was used to estimate allele frequency differences between
winter run and feather river spring.  We also processed the sequence data using
microhaplot (\url{https://github.com/ngthomas/microhaplot}) and visually inspected
loci for consisten allele depth ratio and numbers of haplotypes.  We then chose 24 amplicons for further
testing on the basis of allele frequency differences between Feather River spring run and
winter run, number of haplotypes, and ease of scoring.  These 24 markers were typed on
a variety of fish over the course of a year, and we finally chose three to include in
our California Chinook reference baseline: one amplicon on each of chromosomes
8, 12, and 16.  The estimated frequencies of all the alleles present in the reference baseline
in those three amplicons shows that there are not fixed differences between
winter run and all other reporting units (Table~\ref{tab:wrap-freqs}).
